---
title: "Future Plans for transformr"
author: "Derek McCrae Norton"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Future Plans for transformr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

## Here are some of the possible transforms


### Numeric Transforms

- Box Cox $\lambda_2 = min(y) - 1$?

$$y_{i}^{\lambda} = \cases{\frac{(y_{i} - \lambda_2)^{\lambda_1} - 1}{\lambda_1},& \text{if } \lambda_1 \ne 0 \\ \text{ln }(y_{i} - \lambda_2),& \text{if } \lambda_1 = 0}$$


### Factor Transforms

- Hashing?


### Text Transforms

- Word count
- Average word length
- Sentiment
- ?


### Date Transforms

- Day
- Week
- Month
- Year
- Hour?



